ms2

### 2017-09-01 ms1/ms1_display.Rmd
ms1 fixes

```{r dx_trends}
dx_unadj = read_tsv('tables/dx_trends_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  left_join(select(totals, year, n_bene), by='year') %>%
  mutate(dxpkp=1000*n_dx/n_bene) %>%
  select(dx_cat, year, dxpkp) %>%
  spread(year, dxpkp) %>%
  mutate(unadj_pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

dx_adj = read_tsv('tables/dx_trends.tsv') %>%
  rename(dx_cat=model) %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  model_ci() %>%
  select(dx_cat, change_str, p.value)

full_join(dx_unadj, dx_adj, by='dx_cat') %>%
  kable
```

@@

```{r pde_dx}
read_tsv('tables/dx_from_pde.tsv') %>% 
  spread(present, n) %>%
  mutate(pct=`TRUE`/(`TRUE` + `FALSE`)*100 %>% round(2)) %>%
  select(antibiotic, dx_cat, pct) %>%
  spread(dx_cat, pct) %>%
  kable
```

@@

inner_join(dx_to_pde_unadj, dx_to_pde_adj, by=c('dx_cat', 'antibiotic')) %>%
  # convert model estimates to odds ratios, then to risk ratios,
  # then to adjusted fractional changes, then to percentages
  mutate(or=exp(estimate),
         or_low=exp(ci_low),
         or_high=exp(ci_high),
         rr=risk_ratio_f(or, `2011`),
         rr_low=risk_ratio_f(or_low, `2011`),
         rr_high=risk_ratio_f(or_high, `2011`),
         adj_change=rr-1,
         adj_change_low=rr_low-1,
         adj_change_high=rr_high-1,
         pct_change=(`2014`-`2011`)/`2011`) %>%
  mutate_if(is.numeric, function(x) round(x*100, 2)) %>%
  mutate(adj_change=sprintf('%.2f%% (%.2f -- %.2f%%)', adj_change, adj_change_low, adj_change_high)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, pct_change, adj_change) %>%
  kable
```

>>>>

```{r dx_trends}
dx_unadj = read_tsv('tables/dx_trends_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  left_join(select(totals, year, n_bene), by='year') %>%
  mutate(dxpkp=1000*n_dx/n_bene) %>%
  select(dx_cat, year, dxpkp) %>%
  spread(year, dxpkp) %>%
  mutate(pct_change=(`2014`/`2011`-1)*100) %>%
  arrange(desc(`2011`)) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

dx_adj = read_tsv('tables/dx_trends.tsv') %>%
  rename(dx_cat=model) %>%
  filter(term=='year') %>%
  mult_est(3) %>%
  model_ci() %>%
  select(dx_cat, adj_change=change_str, p.value)

dx_trends = full_join(dx_unadj, dx_adj, by='dx_cat') %T>%
  kable
```

@@

```{r dx_from_pde}
dx_from_pde = read_tsv('tables/dx_from_pde.tsv') %>% 
  spread(present, n) %>%
  mutate(pct=`TRUE`/(`TRUE` + `FALSE`)*100 %>% round(2)) %>%
  select(antibiotic, dx_cat, pct) %>%
  spread(dx_cat, pct) %T>%
  kable
```

@@

dx_to_pde = inner_join(dx_to_pde_unadj,
                       dx_to_pde_adj,
                       by=c('dx_cat', 'antibiotic')) %>%
  # convert model estimates to odds ratios, then to risk ratios,
  # then to adjusted fractional changes, then to percentages
  mutate(or=exp(estimate),
         or_low=exp(ci_low),
         or_high=exp(ci_high),
         rr=risk_ratio_f(or, `2011`),
         rr_low=risk_ratio_f(or_low, `2011`),
         rr_high=risk_ratio_f(or_high, `2011`),
         adj_change=rr-1,
         adj_change_low=rr_low-1,
         adj_change_high=rr_high-1,
         pct_change=(`2014`-`2011`)/`2011`) %>%
  mutate_if(is.numeric, function(x) round(x*100, 2)) %>%
  mutate(adj_change=sprintf('%.2f%% (%.2f -- %.2f%%)', adj_change, adj_change_low, adj_change_high)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, pct_change, adj_change) %T>%
  kable
```

## Combined tables

```{r}
x = dx_trends %>%
  select(-p.value) %>%
  gather('key', 'value', -dx_cat) %>%
  spread(dx_cat, value) %>%
  mutate(antibiotic='dx_trends')

y = dx_from_pde %>%
  mutate(key='dx_from_pde') %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2)))

z = dx_to_pde %>%
  gather('key', 'value', -dx_cat, -antibiotic) %>%
  spread(dx_cat, value)

combined_table = bind_rows(x, y, z) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('dx_trends', top_abx)),
         key=factor(key, levels=c('dx_from_pde', '2011', '2014', 'pct_change', 'adj_change'))) %>%
  arrange(antibiotic, key)
```

### Respiratory stuff

```{r respiratory}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'azithromycin', 'levofloxacin', 'amoxicillin', 'amoxicillin/clavulanate')) %>%
  select(antibiotic, key, not_infectious, asthma, bronchitis, other_resp, pharyngitis, pneumonia, sinusitis, uri) %>%
  kable
```

### UTIs

```{r uti}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'nitrofurantoin')) %>%
  select(antibiotic, key, not_infectious, uti, uti_t3) %>%
  kable
```

### SSTI

```{r ssti}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'clindamycin', 'cephalexin', 'trimethoprim/sulfamethoxazole')) %>%
  select(antibiotic, key, not_infectious, ssti, ssti_t3) %>%
  kable
```

### GI

```{r gi}
combined_table %>%
  filter(antibiotic %in% c('dx_trends', 'ciprofloxacin')) %>%
  select(antibiotic, key, not_infectious, gi, gi_t3) %>%
  kable
```

### 2017-09-01 ms2/ms2_display.Rmd
ms1 fixes

ineq_table %>%
  filter(unit_type=='state') %>%
  # sum across units
  group_by(year, drug_group, n_claims) %>%
  summarize(n_bene=sum(n_bene)) %>%
  ungroup() %>%
  # compute the number of claims made by people making 1 claim, etc.
  mutate(n_class_claims = n_claims * n_bene) %>%
  # compute percentages: fr. of benes w/ 1 claim, fr. of claims made by 1-claimers, etc.
  group_by(year, drug_group) %>%
  mutate(pct_bene=pct(n_bene/sum(n_bene)),
         pct_claims=pct(n_class_claims/sum(n_class_claims))) %>%
  select(year, drug_group, n_claims, pct_bene, pct_claims) %>%
  # group 3+ claims into one group, then sum up fractions in that new group
  mutate(n_claims=fct_other(factor(n_claims), keep=0:2, other_level='3+')) %>%
  group_by(year, drug_group, n_claims) %>%
  summarize_at(vars(pct_bene, pct_claims), sum) %>%
  ungroup() %>%
  # merge the claims group and metric into one key, and spread
  gather('key', 'val', pct_bene:pct_claims) %>%
  mutate(key2=str_c(n_claims, ':', key)) %>%
  select(year, drug_group, key2, val) %>%
  spread(key2, val) %>%
  # keep only 2011 data
  filter(year==2011) %>%
  select(-year) %>%
  kable
```

>>>>

ineq_table %>%
  filter(unit_type=='state') %>%
  # sum across units
  group_by(year, drug_group, n_claims) %>%
  summarize(n_bene=sum(n_bene)) %>%
  ungroup() %>%
  # compute the number of claims made by people making 1 claim, etc.
  mutate(n_class_claims = n_claims * n_bene) %>%
  # compute percentages: fr. of benes w/ 1 claim, fr. of claims made by 1-claimers, etc.
  group_by(year, drug_group) %>%
  mutate(pct_bene=pct(n_bene/sum(n_bene)),
         pct_claims=pct(n_class_claims/sum(n_class_claims))) %>%
  ungroup() %>%
  select(year, drug_group, n_claims, pct_bene, pct_claims) %>%
  # group 3+ claims into one group, then sum up fractions in that new group
  mutate(n_claims=fct_other(factor(n_claims), keep=0:2, other_level='3+')) %>%
  group_by(year, drug_group, n_claims) %>%
  summarize_at(vars(pct_bene, pct_claims), sum) %>%
  ungroup() %>%
  # merge the claims group and metric into one key, and spread
  gather('key', 'val', pct_bene:pct_claims) %>%
  mutate(key2=str_c(n_claims, ':', key)) %>%
  select(year, drug_group, key2, val) %>%
  spread(key2, val) %>%
  # keep only 2011 data
  filter(year==2011) %>%
  select(-year) %>%
  kable
```
